Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-01-23 vesicle_code/docs/adhesion/adhesion.tex
updated figure 1

\begin{figure}[htp]
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/configCartoon.pdf}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances in the
  green region are repulsive and distances in the blue region are
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked in with a red dot is repelled by the green region and
  attracted to the blue region.  The net forces are plotted with the
  black arrows.}
\end{figure}

>>>>

\begin{figure}[htp]
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/adhesionPotential.pdf}
  \end{minipage}
  \hfill
  \begin{minipage}{0.48\textwidth}
    \centering
    \includegraphics[height=6cm]{figs/configCartoon.pdf}
  \end{minipage}
  \caption{\label{fig:adhesionModel} {\em Left}: The adhesion potential
  $\phi(z)$ in Equation~\eqref{eq:adhesion_potential}.  Distances less
  than $\delta$ are repulsive and distances greater than $\delta$ are 
  attractive.  {\em Right}: The resulting adhesive force of a single
  vesicle of a doublet using Equation~\eqref{eqn:adhesionForce}.  The
  point marked with a blue dot is repelled by the region of the vesicle
  denoted with a thick line, and attracted to the remainder of the
  vesicle.  The blue region is repelled to the right vesicle and the red
  region is attracted by the vesicle.}
\end{figure}
